---
title: "Ecosystem Context for Stock Assessments Template"
output: 
        html_document:
                fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rvest)
#stock_name <- 
common_name <- "summer-flounder"

```


# Species Name and Stock Area

Brief written description of the stock

```{r}

# select species codes from survey, fishery, other databases
# code to get geographic footprint, might differ by survey and catch data
# define any other species specific attributes to pass to indicator code below

```


##Temperature (for stock area(s))


##Annual SST for each stock area


##Annual spring/fall BT for each stock area


##Thermal phenology (for stock area(s))


##Spring/fall transition for each stock area


##Chlorophyll concentration (for stock area(s))


##Annual CHL for each stock area


##Zooplankton abundance (for stock area(s))


##Spring/fall abundance of key zooplankton species/groups


##Habitat (for stock area(s))


##Spring/fall occupancy probability for each stock area


##Dynamic sweep area abundance (for stock area(s))


##Spring/fall biomass and abundance


## Historical and Current Distribution 

Kernel density plot
```{r kd, fig.cap= "Kernel density is ..."}
plot_type <- "kd"
url <- sprintf("https://www.nefsc.noaa.gov/ecosys/current-conditions/figures/%s/%s-%s.png",
               plot_type,
               common_name,
               plot_type)

knitr::include_graphics(url)
```


##Prey/predation information


##Fishery/social/economic information




